---
title: "RStudio::conf2020"
date: "Updated: `r format(Sys.Date())`"
output: 
  html_document:
    highlight: zenburn
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../figs",
  gganimate = list(
    nframes = 50
  )
)

```


## Pipeline Packages

Many new options

- [`pins`](https://pins.rstudio.com/) Good for pinning re-useable small datasets
- [`rplumber`](https://www.rplumber.io/) for connecting with APIs


### Teaching

New teaching packages include:

- [`gifski`](https://github.com/r-rust/gifski) animate plots/pngs into gifs
- [`learnr`](https://rstudio.github.io/learnr/) interactive tutorials 
- [`flipbookr`](https://github.com/EvaMaeRey/flipbookr) With [great examples here](https://evamaerey.github.io/ggplot_flipbook/ggplot_flipbook_xaringan.html)
- [`gganimate`](https://github.com/thomasp85/gganimate)


```{r gganim1, message=FALSE, eval=FALSE}

suppressPackageStartupMessages(library(tidyverse))
library(gganimate)
library(gapminder)

tst <- ggplot(data=gapminder, aes(x=gdpPercap, y=lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = FALSE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  facet_wrap(.~continent) +
  # Here comes the gganimate specific bits
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'life expectancy') +
  transition_time(year) +
  ease_aes('linear')
tst
#animate(tst, renderer = ffmpeg_renderer())
```



```{r, eval=FALSE, message=FALSE}

library(gganimate)
p <- ggplot(airquality, aes(Day, Temp)) + 
  geom_line(size = 2, colour = 'steelblue') + 
  transition_states(Month, 4, 1) + 
  shadow_mark(size = 1, colour = 'grey')
animate(p, renderer = ffmpeg_renderer())

```


### Shiny

New options to help format text/design/color, help abstract away writing CSS. Basically take SASS, compile to CSS, but all in R. Can be used with bootstrap bindings, and can be used in `Rmd`, **Shiny**, etc.

```{r newPkgs, eval=FALSE}

library(sass)
#remotes::install_github("rstudio/bootstraplib")
library(bootstraplib)

#remotes::install_github("rstudio/shinymeta")
library(shinymeta)
library(shiny)

```

### Side Projects in R

`@ryantimpe`

@Datasaurs

Leveraging deep learning (keras) in work.

 - rvest
 - ggplot2
 - zoo
 - purrr
 - rtweet
 - twitteR
 - gridExtra
 - brickr
 - keras (Jacqueline Nolis @skyetetra)
 
 
### Plotting in R
 
 SOCCER!! WHAT!?!
 
  - [`ggsoccer`](https://torvaney.github.io/ggsoccer/)
  
## Jenny Bryan: debugging strategies

### Strategies

> **try resetting R**

 - installing/updating packages in R is like working on your airplane while flying
 - start clean R session: `R --no-save --no-restore-data` (NOT `rm(list=ls()))`)
    - any `attach()`, `library()`, `options` and `Sys.setenv(LANGUAGE="fr")` all remain
 - R sessions are like crops, not houseplants

> **work/write a small concrete example that reveals, confirms, or eliminates something (REPREX)**

  - make it inline, small, and as concise
 
> **DEBUG**

`traceback()`, `options(error=recover)`, `browser()`

1. Post mortem: `traceback()`
    - `traceback()`: the callstack in R (backtrace, call trace, etc)
    - `rlang::last_trace()` (see on Debug > On Error > Error Inspector/Recover)
    - When browsing, can use frame (a number), and `ls.str()` to see what environment is
2. Autopsy: `options(error=recover)`
3. Reanimate: `browser`
    - `browser`: start high, and move down, then use `n` for next line, until you get to the stuff you want. And interact with it...*AND* modify it in the browser
    - IDE break points (red dots) good because they don't modify code. `debug` similar but more hampered by not having the source
    
```{r debug, eval=F, include=F}

# to GET OUT: 'Q'
# RStudio Stop Button
# debug() + undebug() so you don't end up in endless browse loop
# debugonce() > only goes into browser once...

```

**Some options:**

 - `testthat::test_that()`
 
 
## Rmarkdown: Rob Hyndman

### How RMarkdown changed my life

Improved speed, simplicity, reproducibility & version control

 - `vitae`- Rmarkdown templates for CVs
 - `robjhyndman/MonashEBSTemplates::memo`
 - `robjhyndman/MonashEBSTemplates::letter`
 - `robjhyndman/MonashEBSTemplates::exams`

## RMarkdown: Yihui

 - css two lines to invert to dark mode
 - add media query to css to respond to operating system mode (dark or light)
 - **pdf/latex:** 
 
## ggplot

 - adding variable names within `aes()` and `vars()`: `.data[["variable_name"]]`
 - adding `NULL` doesn't change anything: `ggplot() + NULL` == `ggplot()`
 - can add ggplot layers as a list: `ggplot() + 1 + 2 + etc` == `ggplot()+list(1,2)`
 - Slides: *fishandwhistle.net/slides/rstudioconf2020*
 - Code: github.com/paleolimbot/rstudioconf2020
 
 
## Tidy Tuning: Max Kuhn

### Pre-processing with [{`recipes`}](https://tidymodels.github.io/recipes/)

Helps to create a blueprint for your model, here create a simple recipe containing only an outcome and predictors and have the predictors centered and scaled:

```{r recipes, echo=TRUE, eval=FALSE}

library(recipes)
library(tidymodels)
library(AmesHousing)
ames <- make_ames()
set.seed(4595)
data_split <- initial_split(ames, strata = "Sale_Price", p = 0.75)

ames_train <- training(data_split)
ames_test  <- testing(data_split)

# make a recipe
norm_recipe <- 
  recipe(
    Sale_Price ~ Longitude + Latitude + Lot_Area + Neighborhood + Year_Sold, 
    data = ames_train
  ) %>%
  step_other(Neighborhood) %>% 
  step_dummy(all_nominal()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_log(Sale_Price, base = 10) %>% 
  # estimate the means and standard deviations
  prep(training = ames_train, retain = TRUE)


```


### Creating Models with [{`parsnip`}](https://tidymodels.github.io/parsnip/)

```{r parsnip, eval=FALSE}

library(parsnip)
library(glmnet)

# Now let's fit the model using the processed version of the data

glmn_fit <- 
  linear_reg(penalty = 0.001, mixture = 0.5) %>% 
  set_engine("glmnet") %>%
  fit(Sale_Price ~ ., data = juice(norm_recipe))
summary(glmn_fit)

```

Tuning package allows you to find good values for paraemters for penalty, mixture...how can we alter these objects to "tag" which arguments we should tune?

```{r eval=FALSE}
# First, get the processed version of the test set predictors:
test_normalized <- bake(norm_recipe, new_data = ames_test, all_predictors())

test_results <- 
  test_ %>%
  rename(`random forest` = .pred) %>%
  bind_cols(
    predict(glmn_fit, new_data = test_normalized) %>%
      rename(glmnet = .pred)
  )

test_results
```


### Tuning with [{`tune`}](https://tidymodels.github.io/tune/)

```{r eval=FALSE, echo=TRUE}
# library(tune) # also in tidymodels
```


## tidyeval: Lionel

1. Unexpected masking
 
```{r}
library(dplyr)
# solution be explicit
n <- 100
data <- data.frame(x=1, n=2)
data %>% 
  mutate(y=.data$x / .env$n)

```
 
 
2. Data-variables through arguments

```{r}

library(dplyr)

mean_by<- function (data, by, var) {
  data %>% 
    group_by({{by}}) %>% 
    summarize(varmean = mean({{var}}, na.rm = TRUE))
}

mean_by(mtcars, gear, mpg)

```

## ggtext

```{r, eval=F}
library(cowplot)
library(ggtext)
library(ggplot2)
library(units)

ggplot(data=mpg, aes(x=cty, y=hwy)) + 
  geom_point() +
  facet_grid(cyl~class) +
  theme_half_open(12) +
  background_grid() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_textbox(
      size = 12,
      color = "white", fill = "#5D729D", box.color = "#4A618C",
      halign = 0.5, linetype = 1, 
      r = unit(5, "points"), 
      width = unit(1, "npc"),
      padding = margin(2, 0, 1, 0), margin = margin(3, 3, 3, 3)),
    strip.text.y = element_textbox(
      size = 10, halign = 0.5, 
      color = "white", fill = "#5D729D", box.color = "#4A618C",
      linetype = 1, 
      r = unit(5, "points"), width = unit(.25, "npc"),
      padding = margin(1, 1, 1, 1), margin = margin(1, 1, 1, 1)
    )
  )

```

## {`slider`}

## {`wavesurfer`}

## Visual Notetaking/Sketch Noting

 - 1. Leave s p a c e
 - 2. font hierarchy: (**bold**, *italic*, big, small)
      - Title, heading, start, normal
 - 3. Pens: regular, thicker, colors
 - 4. Blotter/thick paper
 - 5. Visual vocabulary: (see here: https://cran.r-project.org/web/packages/emojifont/vignettes/emojifont.html)
 
```{r, eval=TRUE, echo=F}
library(icon)
```

 
 `r fa_rocket(color = "#1FA67A")` + `r fa_r_project(color = "#384CB7")` = `r ai_acclaim()`
    
    